Learning Network Size while Training with ShrinkNets

### 2018-02-09 paper/ICML/introduction.tex

In summary, our contributions are as follows: 
\begin{compactenum}
\item We propose a novel technique based on dynamically switching on and off neurons, 
which allows us to optimize the network size as the network is trained. 
\item \srm{xxx postprocessing techniques to strip out switch layers}
\item We show that our technique is a relaxation of group LASSO~\cite{Yuan2006} and prove that our problem admits many global minima.
\item We demonstrate the efficacy of our technique on both convolutional and fully-connected neural nets,
showing that 
ShrinkNets finds networks within +/-X\% of best hand-crafted accuracy in XX\% of
training time compared to existing hyperparameter optimization methods. \srm{Mention the specific 
model/dataset where this is true.}
\item We demonstrate that ShrinkNets can achieve this accuracy with only YY\% 
of neurons. \srm{This claim should be something about how much smaller a network with say 99\%
accuracy is one some real dataset}
\item \srm{Some claim about inference time}
\item \srm{Some claim about model size vs performance}
\end{compactenum}

>>>>

In summary, our contributions are as follows:

\begin{compactenum}

\item We propose a novel technique based on dynamically switching on and off neurons, 
which allows us to optimize the network size while the network is trained.

\item We implement our technique so as to remove entire neurons, therefore
leading not only to small and well-performing networks, but also dense, which
means higher inference performance.

%\item \srm{xxx postprocessing techniques to strip out switch layers}

\item We show that our technique is a relaxation of group LASSO~\cite{Yuan2006}
and prove that our problem admits many global minima.

\item We demonstrate our claims with both fully-connected and convolutional well
known neural network architectures. We show that with ShrinkNets for
\texttt{CIFAR10} we achieve the same accuracy than a traditionally trained
network while reducing the network size by a factor of $2.2x$. Further, when
willing to sacrifice only $1$\% of performance, ShrinkNets finds networks which
are 35\% smaller. All in all, this leads to speedups in inference time of up to
40X.

%\item We demonstrate the efficacy of our technique on both convolutional and
%fully-connected neural nets, showing that ShrinkNets finds networks within
%+/-X\% of best hand-crafted accuracy in XX\% of training time compared to
%existing hyperparameter optimization methods. \srm{Mention the specific
%model/dataset where this is true.}

%\item We demonstrate that ShrinkNets can achieve this accuracy with only YY\% of
%neurons. \srm{This claim should be something about how much smaller a network
%with say 99\% accuracy is one some real dataset}
%
%\item \srm{Some claim about inference time}
%
%\item \srm{Some claim about model size vs performance}

\end{compactenum}
